Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-08-17 EMNLP-demo-paper/NLPVis-demo-paper.tex
grammar check for nlp paper

\begin{abstract}
Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme. Despite their advantages, the lack of interpretability hinders the deployment and refinement of the models. In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions which in turn shed light on the model decision-making processing.
\end{abstract}

>>>>

\begin{abstract}
Neural networks models have gained unprecedented popularity in natural language processing due to their state-of-the-art performance and the flexible end-to-end training scheme. Despite their advantages, the lack of interpretability hinders the deployment and refinement of the models. In this work, we present a flexible visualization library for creating customized visual analytic environments, in which the user can investigate and interrogate the relationships among the input, the model internals (i.e., attention), and the output predictions, which in turn shed light on the model decision-making process.
\end{abstract}

### 2018-08-17 EMNLP-demo-paper/conclusion.tex
grammar check for nlp paper

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allow the user to interrogate the relationship between different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of the tool by configuring the visual components to investigate models for different NLP tasks (e.g., NLI, MC).
%
We also conducted a small-scale user evaluation, in which five Ph.D. level students with NLP background spent 30 minutes with the tool and then provided feedback. Most suggested the environment allowed them to refine queries iteratively and identify potential issues with the model, but some also mentioned the tool might not provide enough guidance for users who do not have an in-depth understanding of the model at hand.

Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, it is hard to ensure compatibility with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such as neural machine translation and more.

>>>>

\section{Discussion}
In this work, we introduce a visualization library for creating customized environments that allows the user to interrogate the relationships among different parts of the model pipeline via interactive queries.
%
We demonstrate the usability and flexibility of the tool by configuring the visual components to investigate models for different NLP tasks (e.g., NLI, MC).
%
We also conducted a small-scale user evaluation, in which five Ph.D.-level students with an NLP background spent 30 minutes with the tool and then provided feedback. Most suggested the environment allowed them to refine queries iteratively and identify potential issues with the model, but some also mentioned the tool might not provide enough guidance for users who do not have an in-depth understanding of the model at hand.

Even though we designed the individual components with versatility in mind, due to a large number of variants of attention networks, we found it difficult to ensure compatibility with all the available configurations.
%
In the future, we plan to improve upon the current attention interface, release the library as an open-source package, and expand the visualization components to handle tasks such as neural machine translation and more.

### 2018-08-17 EMNLP-demo-paper/intro.tex
grammar check for nlp paper

Deep neural networks have been successfully applied to various natural language processing tasks.
%where end-to-end training become a primary option.
As the design of neural networks evolves, there is a clear trend of increasing model complexity in terms of both the architecture and the parameter count. 
%
While expressive models help improve the prediction performance, the fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
%
The ability to interpret model internals and reason about predictions is essential for understanding the limitation of the models and improving upon them.

@@

Recently, the attention networks have become  widely-adopted~\cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}. It not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words). As a result, attention can provide a natural interface for analyzing the internals of neural networks. Conducting analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as bipartite graph and heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.  However, many challenges remain. Firstly, for some NLP tasks, the word sequences pair for which the attention is computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), which the standard visual encoding cannot adequately handle.  Also, many previous works present the attention in a static setting. However, the ability to provide an interactive environment, in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction, is crucial for interpreting the model. Finally, many previous visualization efforts, despite revealing many exciting results, focus more on illustrating potentially useful visualization techniques than on providing a flexible software tool that can be easily integrated into an existing code base. As a result, applying these proposed techniques to real-world examples may involve substantial engineering effort that could prevent wide adoption.

>>>>

Deep neural networks have been successfully applied to various natural language processing tasks.
%where end-to-end training become a primary option.
As the design of neural networks evolves, there is a trend of increasing model complexity become clear in terms of both the architecture and the parameter count. 
%
Although expressive models help improve the prediction performance, the fundamental lack of interpretability leads many researchers to consider neural network models black boxes. 
%
The ability to interpret model internals and reason about predictions is essential for understanding the limitation of the models and improving upon them.

@@

Recently, the attention networks have recently become  widely-adopted~\cite{bahdanau2014neural,seo2016bidirectional,Parikh2016, VaswaniShazeerParmar2017}. Attention not only improves the model performance but also yields interpretable intermediate representations (i.e., alignment among words). As a result, attention can provide a natural interface for analyzing the internals of neural networks. Conducting analysis directly on the raw attention values can be challenging for human users, and therefore, visual representations that highlight word alignments between sentences have been proposed, such as the bipartite graph and the heatmap of the attention matrix \cite{LiChenHovy2015, li2016understanding, lee2017interactive}.  However, many challenges remain. Firstly, for some NLP tasks, the word sequences pair for which the attention is computed can be highly asymmetrical (i.e., in machine comprehension, the context paragraph can be much longer than the question sentence), which the standard visual encoding cannot adequately handle.  Also, many previous works present the attention in a static setting. However, the ability to provide an interactive environment in which the user can instantaneously look at how changes in the input affect the attention, and how small variations in the attention alter the prediction, is crucial for interpreting the model. Finally, many previous visualization efforts, despite revealing many exciting results, focus more on illustrating potentially useful visualization techniques than on providing a flexible software tool that can be easily integrated into an existing code base. As a result, applying these proposed techniques to real-world examples may involve substantial engineering effort, which could prevent wide adoption.

### 2018-08-17 EMNLP-demo-paper/relatedWorks.tex
grammar check for nlp paper

\section{Related Works}
Due to the increasing demand for model interpretability, many previous works have been proposed for making sense of NLP models by examining individual predictions as well as the model mechanism as a whole. 
%
In recent work,~\citet{LiChenHovy2015} investigated the composability of the vector-based text representations using instance-level attribution techniques originated from the vision community~\cite[e.g.,][]{ZeilerFergus2014}. 
%
In a study of the representation of erasure, \citet{li2016understanding} explained neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units, or input words) on the prediction performance.

Besides interpreting the model via carefully designed experiments, several interactive demo/visualization systems, such as AllenNLP's demos (\url{http://demo.allennlp.org/})  often rely on visual encodings to summarize the model predictions. They  provide a flexible environment in which the user can experiment with the various inputs and perform error analysis.
%The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and 
The hidden state properties of the LSTM are visualized and investigated in the LSTMvis visualization system \cite{StrobeltGehrmannPfister2018}.
\citet{lee2017interactive} visualized the beam search and attention component in neural machine translation models, in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
In the visualization work on question answering~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answers the question. 
%The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.

>>>>

\section{Related Works}
Due to the increasing demand for model interpretability, many previous works have been proposed for making sense of NLP models by examining individual predictions as well as the model mechanism as a whole. 
%
In recent work,~\citet{LiChenHovy2015} investigated the composability of the vector-based text representations using instance-level attribution techniques that originated from the vision community~\cite[e.g.,][]{ZeilerFergus2014}. 
%
In a study of the representation of erasure, \citet{li2016understanding} explained neural model decisions by exploring the impact of altering or removing the components of the model (i.e., changing the dimension count of hidden units or input words) on the prediction performance.

Besides interpreting the model via carefully designed experiments, several interactive demo/visualization systems, such as AllenNLP's demos (\url{http://demo.allennlp.org/}), often rely on visual encodings to summarize the model predictions. These systems provide a flexible environment in which the user can experiment with the various inputs and perform error analysis.
%The training dynamic of RNN network is visualized in the RNNbow system~\cite{CashmanPattersonMosca2017}, and 
The hidden state properties of the LSTM are visualized and investigated in the LSTMvis visualization system \cite{StrobeltGehrmannPfister2018}.
\citet{lee2017interactive} visualized the beam search and attention component in neural machine translation models, in which the user can dynamically change the probability for the next step of the search tree or change the weight of the attention.
In the visualization work on question answering~\cite{ruckle2017end}, the system shows the text context and highlights the critical phrase that is used to answer the question. 
%The user is able to use the visual feature to compare the benefit and drawback of multiple attention based neural network model.

### 2018-08-17 EMNLP-demo-paper/result.tex
figure spacing
grammar check for nlp paper

%\begin{figure*}[t]
%\centering
%\vspace{-2mm}
% \includegraphics[width=1.0\linewidth]{NLI_MC_interface}
%  \vspace{-6mm}
% \caption{
%Illustration of different configurations for the natural language inference and machine comprehension tasks.
%}
%\label{fig:pipelineUpdate}
%\end{figure*}
\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{NLIexample}
  \vspace{-7mm}
 \caption{
An illustration of the attention editing process.
The dependency structure is shown in (a), where the two ``greens'' decorate different nouns.
By removing the ``wrong'' alignment in (b), the original prediction \emph{entailment} is corrected to \emph{neutral} in (c).
}
\vspace{-2mm}
\label{fig:NLIexample}
\end{figure*}

@@

\subsection{Machine Comprehension}
\label{sec:MCexample}
In the machine comprehension task, the goal is to select a span of text as the answer
to a question sentence.
%two sequences of texts are given: context and question.
%The goal is to select a span of text from the context that answers the question. 
%We provide a simple model formulation and refer the reader to the paper for details.
%%\begin{align}
%	$C^\prime, Q^\prime = BiLSTM(C), BiLSTM(Q)$,
%	$\overleftarrow{A} = u(C^\prime, Q^\prime)$,
%	$\overrightarrow{A} = v(C^\prime, Q^\prime)$,
%	$s = m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%	$e = n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%%\end{align}
%where $C$ and $Q$ are embedding matrices for the context and the question,
%$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
%$s$ and $e$ are probabilities for starting and ending indices of the answer span.
%Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
%$s$ and $e$.
The attention information is encoded as a bi-directional alignment (i.e., from context to question and vice versa). 
%The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
Here, we refer the context to question attention as \emph{att1}; and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}). In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values.

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{MC_interface}
  \vspace{-7mm}
 \caption{
In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrates the predicted start and end index of the answer in the context (the deeper the red, the higher the probability). The most likely answer is shown in ($a1$). The global attention and local attention are visualized by ($a2$, $a3$).
%
We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$). As illustrated in ($b1$, $b2$), by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question). 
}
\label{fig:MCexample}
\end{figure*}

As illustrated in Figure~\ref{fig:MCexample}, we represent \emph{att2} as colored bars with a \emph{yellow-green-blue} colormap. Each rectangular bar corresponds to one sentence. The user can focus on individual sentences by clicking on the rectangular bar (see Figure~\ref{fig:MCexample}).
%The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted probabilities of the start and the end index for the answer (the deeper the higher). %The span of text defined by the beginning and end index with the highest probability is the answer.
%
%In Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities. 
In Figure~\ref{fig:MCexample}(a3), the sentence containing the answer exhibits good alignment with the question (e.g., ``Two'' with ``many'').
%In (a3), we examine the sentence that contains the answer, which exhibits excellent alignment with the question (e.g., ``Two'' is aligned with ``many''). 
%The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
Interestingly, the number ``9'' (in ``Falcon 9') is also aligned with ``many'', which may lead to problems.

The user can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
%
As illustrated in ($b1$, and $b2$), the perturbation removes the word ``partial'' in the original sentence, which leads the model to produce a different yet correct answer (``No''). Referring to ($a1$), we can see the word ``No'' exhibits the second highest probability for the original question.
%
The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from ``how many'' to ``which''.
%One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.

>>>>

%\begin{figure*}[t]
%\centering
%\vspace{-2mm}
% \includegraphics[width=1.0\linewidth]{NLI_MC_interface}
%  \vspace{-6mm}
% \caption{
%Illustration of different configurations for the natural language inference and machine comprehension tasks.
%}
%\label{fig:pipelineUpdate}
%\end{figure*}
\begin{figure*}[t]
\centering
 \includegraphics[width=1.0\linewidth]{NLIexample}
  \vspace{-6mm}
 \caption{
An illustration of the attention editing process.
The dependency structure is shown in (a), where the two ``greens'' decorate different nouns.
By removing the ``wrong'' alignment in (b), the original prediction \emph{entailment} is corrected to \emph{neutral} in (c).
}
\label{fig:NLIexample}
\end{figure*}

@@

\begin{figure*}[t]
\centering
 \includegraphics[width=1.0\linewidth]{MC_interface}
  \vspace{-6mm}
 \caption{
In the machine comprehension visualization interface (a), the $p1$, $p2$ colored bar (in $a3$) illustrates the predicted start and end index of the answer in the context (the deeper the red, the higher the probability). The most likely answer is shown in ($a1$). The global attention and local attention are visualized by ($a2$, $a3$).
%
We can evaluate the robustness of the prediction by perturbing the question sentence ($b1$, $b3$). As illustrated in ($b1$, $b2$), by removing the word ``partial'', the model still finds the correct answer (albeit different, as the sentence perturbation changes the exact meaning of the question). 
}
\vspace{-2mm}
\label{fig:MCexample}
\end{figure*}

\subsection{Machine Comprehension}
\label{sec:MCexample}
In the machine comprehension task, the goal is to select a span of text as the answer
to a question sentence.
%two sequences of texts are given: context and question.
%The goal is to select a span of text from the context that answers the question. 
%We provide a simple model formulation and refer the reader to the paper for details.
%%\begin{align}
%	$C^\prime, Q^\prime = BiLSTM(C), BiLSTM(Q)$,
%	$\overleftarrow{A} = u(C^\prime, Q^\prime)$,
%	$\overrightarrow{A} = v(C^\prime, Q^\prime)$,
%	$s = m(C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%	$e = n(s, C^\prime, Q^\prime, \overleftarrow{A}, \overrightarrow{A})$,
%%\end{align}
%where $C$ and $Q$ are embedding matrices for the context and the question,
%$\overleftarrow{A}$ and $\overrightarrow{A}$ are bidirectional attention flows,
%$s$ and $e$ are probabilities for starting and ending indices of the answer span.
%Our system reveals the internal states of $\overleftarrow{A}$, $\overrightarrow{A}$,
%$s$ and $e$.
The attention information is encoded as a bidirectional alignment (i.e., from context to question and vice versa). 
%The key difference is how the question to context alignment is computed (see \cite{Seo2016} for more details).
Here, we refer the context to question attention as \emph{att1} and the question to context attention as \emph{att2} (which is a vector instead of a matrix according to \citet{Seo2016}). In this demo, we apply a min max normalization for \emph{att2} after the softmax layer to better distinguish different attention values.

As illustrated in Figure~\ref{fig:MCexample}, we represent \emph{att2} as colored bars with a \emph{yellow-green-blue} colormap. Each rectangular bar corresponds to one sentence. The user can focus on individual sentences by clicking on the rectangular bar (see Figure~\ref{fig:MCexample}).
%The proposed visualization help reveal the potential alignment issues in the machine comprehension model.
The $p1$, $p2$ colored bars (\emph{white-red} colormap) illustrate the predicted probabilities of the start and the end index for the answer (the deeper the higher). %The span of text defined by the beginning and end index with the highest probability is the answer.
%
%In Figure~\ref{fig:MCexample} ($a3$), there are two spans of text that correspond to higher probabilities. 
In Figure~\ref{fig:MCexample}(a3), the sentence containing the answer exhibits good alignment with the question (e.g., ``Two'' with ``many'').
%In (a3), we examine the sentence that contains the answer, which exhibits excellent alignment with the question (e.g., ``Two'' is aligned with ``many''). 
%The spans of text with high probability are ``Two'' and ``No'' (highlight in orange), both align well with the word ``many''.
Interestingly, the number "9" (in "Falcon 9") is also aligned with "many", which may lead to problems.

The user can explore the robustness of the model by examining how the prediction varies when the question is perturbed.
%
As illustrated in ($b1$, and $b2$), the perturbation removes the word "partial" in the original sentence, which leads the model to produce a different yet correct answer ("No"). Referring to ($a1$), we can see the word "No" exhibits the second highest probability for the original question.
%
The user can also manually edit the text. As shown in ($b3$), the model still produces the correct answer when changing the question from "how many" to "which".
%One possible explanation is that the word ``Two'' has a much higher \emph{att2} attention value compared to ``9'', which may contribute to the current outcome.

### 2018-08-17 EMNLP-demo-paper/system.tex
figure spacing
grammar check for nlp paper

\section{Visualization System}
As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP models follow a similar encoder--attention--classifier structure. The attention stage provides a window to peek into the model decision making process. 
However, the static attention alone does not tell the whole story. 
Our proposed system uses a perturbation-driven exploration strategy that allows the user manually or automatically perturb part of the pipeline and observe the changes downstream.
%
The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task. In the following section, we will cover some of the essential components; the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=PKiM4i0oIuY}{link}.
%such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

@@

To improve the perturbation quality, we also allow for a translation-based paraphrasing technique similar to \citet{mallinson2017paraphrasing}. Here, we translate the original English sentence into several other languages and then pivot back to English. Provided the translation produces good result (in our case, we use the Google cloud translation platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.8\linewidth]{prediction}
 \caption{
Summary of the prediction results of the perturbed input for the natural language inference model.
The prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label.
}
\vspace{-3mm}
\label{fig:prediction}
\end{figure}

@@

For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded via a triangular barycentric coordinate system, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}). The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.

@@

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{attentionPanels}
  \vspace{-3mm}
 \caption{
Attention visualization. A bipartite graph encoding is adopted in the graph attention view (a), in which the edge thickness corresponds to the attention value. The same attention values can also be directly visualized in the matrix form (b).
The user can edit the attention values via the pop-up interface illustrated in (c).
We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentences (shown in the video).
%
For highly asymmetric attention, we utilized a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting the summary visualization.
}
\vspace{-3mm}
\label{fig:attentionVis}
\end{figure*}

@@

\subsection{Implementation}
The initial setup cost and unnecessary learning curve are often the barriers to broad adaptation of a tool. 
Therefore, instead of designing a visualization system as a monolithic standalone application, 
we implement the proposed system as a Python library with modularity and ease of use in mind.
The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually, 
or combined with other components to fit one's work-flow via a simple API.
More importantly, the library-based design allows easy integration with the existing model implemented in python.
%To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models. 
The code for creating an interactive exploration environment for a machine comprehension model is illustrated below.

>>>>

\section{Visualization System}
As illustrated in Figure~\ref{fig:modelPipeline}, many recent end-to-end NLP models follow a similar encoder--attention--classifier structure. The attention stage provides a window to peek into the model decision-making process. 
However, the static attention alone does not tell the whole story. 
Our proposed system uses a perturbation-driven exploration strategy that allows the user to manually or automatically perturb part of the pipeline and observe the changes downstream.
%
The system consists of several visualization components that can be selectively combined to form a functional interactive system for a given task. In the following section, we will cover some of the essential components; the usage of all components can be found in the accompanying video \href{https://www.youtube.com/watch?v=PKiM4i0oIuY}{link}.
%such as a prediction summary statistics the entire development set, as well as a scheme to update the model based

@@

To improve the perturbation quality, we also allow for a translation-based paraphrasing technique similar to that proposed by \citet{mallinson2017paraphrasing}. Here, we translate the original English sentence into several other languages and then pivot back to English. Provided the translation produces a good result (in our case, we use the Google Cloud Translation Platform), we can obtain paraphrases of the original sentence (see Figure~\ref{fig:sentence}, where the drop-down menu shows some of the perturbed sentences).

\begin{figure}[htbp]
\centering
%\vspace{-2mm}
 \includegraphics[width=0.8\linewidth]{prediction}
 \caption{
Summary of the prediction results of the perturbed input for the natural language inference model.
The prediction is encoded as a point in the barycentric coordinate system of the triangle, in which each vertex corresponds to one prediction label.
}
\vspace{-3mm}
\label{fig:prediction}
\end{figure}

@@

For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded via a triangular barycentric coordinate system, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}). The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller gray circles.

@@

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{attentionPanels}
  \vspace{-3mm}
 \caption{
Attention visualization. A bipartite graph encoding is adopted in the graph attention view (a), in which the edge thickness corresponds to the attention value. The same attention values can also be directly visualized in the matrix form (b).
The user can edit the attention values via the pop-up interface illustrated in (c).
We overlay the dependency tree ($a_1$) grammar structure to highlight important words and allow simplification of complex sentences (shown in the video).
%
For highly asymmetric attention, we utilize a zoomable hierarchical visual representation (d). The user can focus on the individual sentence by selecting the summary visualization.
}
\vspace{-3mm}
\label{fig:attentionVis}
\end{figure*}

@@

\subsection{Implementation}
The initial setup cost and unnecessary learning curve are often the barriers to broad adaptation of a tool. 
Therefore, instead of designing a visualization system as a monolithic standalone application, 
we implement the proposed system as a Python library with modularity and ease of use in mind.
The different pieces of the visualization (i.e., matrix-based attention encoding) can be accessed individually or combined with other components to fit one's workflow via a simple API.
More importantly, the library-based design allows easy integration with the existing model implemented in Python.
%To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models. 
The code for creating an interactive exploration environment for a machine comprehension model is illustrated below.
